Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-03 tese/section01.tex
14 pages, DTLS, TLS, SRTP, SCTP

>>>>

\ac{TLS} doesn't support independent record decryption, for that it requires a reliable transport channel, tipically \ac{TCP}. The decryption of a record depends on the previous record, which for unreliable transport protocols like \ac{UDP} may represent a problem, either due to packet loss or different receival order.

\ac{DTLS} is similar to \ac{TLS} but on top of \ac{UDP}, the main difference is the inclusion of a sequence number per packet that is used for packet re-ordering on receival and protects from duplicated packets. If a packet sequence number is less then the expected sequence number, the packet is discarded. If a packet sequence number is greater than the expected sequence number, the packet may be enqueued or discarded. By knowing the sequence of messages that are sent and received in \ac{TLS}, timers are used for packet retransmission avoiding ackowledgement messages.

\ac{WebRTC}'s \textit{Data Channel} is built on top of \ac{SCTP}, which is secured by \ac{DTLS}. A \textit{Data Channel} has one incoming stream and one outgoing stream, providing bidirectional communication. Each data channel direction can be tweaked for reliable or unreliable transmission, the same can be done for order delivery. A priority can also be defined for improving the quality of service for a particular stream compared to another.

### 2015-05-03 tese/section04.tex
14 pages, DTLS, TLS, SRTP, SCTP

@@

  {\color{red}[DTLS and SRTP]}

  \ac{RTP} recorders are independent of payload encoding, they don't decode \ac{RTP} packets, they record packets instead, allowing to record all video and audio formats.

>>>>

\ac{RTCP} is used for controlling \ac{RTP} multimedia streams, it provides bandwidth statistics and control information that can be used for changing the quality of the stream in real time.

@@

  Another profile for \ac{RTP} is defined by \ac{SRTP}, which provides encryption, authentication and replay protection of \ac {RTP} traffic. The analogous secure protocol for \ac{RTCP} is \ac{SRTCP}.

  Both \ac{SRTP} and \ac{SRTCP} uses \ac{AES} by default, which is symmetric-key algorithm for data encryption. Each packet is encrypted using a distinct keystream, otherwise using a single keystream with \ac{AES} on \ac{CBC} would make impossible to recover from packet loss.

  wo keystream generators for \ac{AES} were defined: \textit{Segmented Integer Counter Mode} and \textit{f8-mode}. If a packet is lost, there is no impact on other packets, as the initialization vector is obtained through those keystream generators and it's fixed for each packet.

  \ac{RTP} recorders are independent of payload encoding, they don't decode \ac{RTP} packets, they record packets instead, allowing to record all video and audio formats even if they're encrypted.
